Appendix S2: Data Exploration

### 2022-04-27 ms/data_exploration.Rmd

So we will conservatively only remove the grid-cell with unusually high % apomictic taxa, then run Grubb's test again.

@@

biodiv_ferns_cent_no_outliers %>%
  pull(percent_apo) %>%
  grubbs_tidy()
```

OK, no more outliers in `percent_apo`.

>>>>

So we will conservatively only remove the single grid-cell with most % apomictic taxa, and inspect the data.

@@

biodiv_ferns_cent_no_outliers %>%
  arrange(desc(percent_apo)) %>%
  select(percent_apo, richness)
```

That seems more reasonable.
